---
title: "CourseraCourse"
author: "Marton Toth"
date: '2016 november 5 '
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(grid)
knitr::opts_chunk$set(echo = TRUE)
```

1. Code for reading in the dataset and/or processing the data
Removing NAs in addition to

```{r}
data<-read.csv("activity.csv")
data<-data[complete.cases(data),]
summary(data)
head(data)
```

2. Histogram of the total number of steps taken each day

```{r}
sumStepsByDate<-aggregate(steps~date, data=data, FUN = sum)
hist(sumStepsByDate$steps, breaks=10, main="Histogram of number of steps taken in a day", xlab="Total number of steps taken in a day")
```

3. Mean and median number of steps taken each day
```{r}
mean(sumStepsByDate$steps)
median(sumStepsByDate$steps)
```
4. Time series plot of the average number of steps taken
```{r}
avgStepsByDate<-aggregate(steps~date, data=data, FUN = sum)
barplot(avgStepsByDate$steps, names = avgStepsByDate$date,
  xlab = "Date", ylab = "Average number of steps",
  main = "Average number of steps taken")
```

5. The 5-minute interval that, on average, contains the maximum number of steps
The calculation of means for each interval:
```{r}
splitByInterval<-with(data,split(steps,interval))
meanByInterval<-lapply(splitByInterval, mean)
meanByInterval<-unlist(meanByInterval)
```
The interval containing the maximum value:
```{r}
which(meanByInterval==max(meanByInterval))
```
The time of day this interval begins is 13.55
```{r}
835%/%60
835 %% 60
```
The mean value of steps taken in this interval:
```{r}
max(meanByInterval)
```

6. Code to describe and show a strategy for imputing missing data
Replacing NA values with mean values for corresponding intervall
```{r}
data<-read.csv("activity.csv")
    X=data[,1]
    Y<-rep(meanByInterval,length.out=17568)
    X<-ifelse(!is.na(X),X,Y)
    data[,1]=X
  
```
7. Histogram of the total number of steps taken each day after missing values are imputed

Since w 
```{r}
sumStepsByDate<-aggregate(steps~date, data=data, FUN = sum)
hist(sumStepsByDate$steps, breaks=10, main="Histogram of number of steps taken in a day", xlab="Total number of steps taken in a day")
```

8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}

averageInterval <- function(data ){
    splitByInterval<-with(data,split(steps,interval))
    meanByInterval<-lapply(splitByInterval, mean) 
    meanByInterval<-unlist(meanByInterval)
    return(meanByInterval)
}

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

data$date<-as.POSIXlt(data$date,format="%Y-%m-%d")

weekendData<-subset(data, weekdays(as.Date(data$date)) %in% c("Saturday","Sunday"))
weekdayData<-subset(data, !weekdays(as.Date(data$date)) %in% c("Saturday","Sunday"))

weekendData<-averageInterval(weekendData)
weekdayData<-averageInterval(weekdayData)

weekendFrame<-data.frame(keyName=names(weekendData), value=weekendData, row.names=NULL)
weekdayFrame<-data.frame(keyName=names(weekdayData), value=weekdayData, row.names=NULL)

p1 <- ggplot(weekendFrame, aes(x=keyName, y=value, group=1)) +
    geom_line(colour="blue", lwd=1) +
    ggtitle("Average Number of Steps Taken on Weekends") +
    labs(x="Intervals", y="Number of steps")

p2 <- ggplot(weekdayFrame, aes(x=keyName, y=value, group=1)) +
    geom_line(colour="red",lwd=1) +
    ggtitle("Average Number of Steps Taken on Weekdays") +
    labs(x="Intervals", y="Number of steps")

multiplot(p1,p2)
```
